\documentclass[10pt, a4paper]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{1.5ex}{1ex}

\begin{document}
\pagestyle{empty}

\begin{center}
    {\Huge \textbf{Lucia Fernandez}} \\
    \vspace{0.5ex}
    Barcelona, Spain $\cdot$ lucia.fernandez@email.com $\cdot$ +34 611 111 111 \\
    \href{https://github.com/luciaf}{github.com/luciaf} $\cdot$ \href{https://portfolio.luciaf.dev}{portfolio.luciaf.dev}
\end{center}

\section*{Education}
\textbf{Universitat de Barcelona (UB)} \hfill Sep 2021 -- Jun 2025 \\
\textit{B.S. in Computer Science} \hfill Barcelona, Spain
\begin{itemize}[leftmargin=0.2in, nosep]
    \item \textbf{Relevant Coursework:} Data Structures, Algorithms, Machine Learning, Database Systems, Operating Systems.
    \item \textbf{Honors:} Dean's List (2022, 2023), 1st Place in UB Hackathon 2024.
\end{itemize}

\section*{Technical Skills}
\begin{itemize}[leftmargin=0.2in, nosep]
    \item \textbf{Languages:} C++, Python, JavaScript, SQL.
    \item \textbf{Technologies:} React, Flask, Pandas, Scikit-Learn, Git, Linux/Unix.
\end{itemize}

\section*{Projects}
\textbf{Smart Campus Navigation App} $|$ \textit{React Native, Python, Firebase} \hfill Jan 2025 -- May 2025
\begin{itemize}[leftmargin=0.2in, nosep]
    \item Developed a cross-platform mobile application assisting visually impaired students in navigating the university campus.
    \item Implemented A* pathfinding algorithm on the backend to calculate optimal routes, reducing average travel time by 15\%.
\end{itemize}
\vspace{1ex}
\textbf{Predictive Stock Analysis Tool} $|$ \textit{Python, Pandas, Scikit-Learn} \hfill Oct 2024 -- Dec 2024
\begin{itemize}[leftmargin=0.2in, nosep]
    \item Built a machine learning pipeline to predict short-term stock movements using historical market data.
    \item Trained and tuned Random Forest and XGBoost models, achieving a 68\% directional accuracy on test data.
\end{itemize}

\section*{Experience}
\textbf{Software Engineering Intern} \hfill Jun 2024 -- Sep 2024 \\
\textit{InnoTech Startups} \hfill Barcelona, Spain
\begin{itemize}[leftmargin=0.2in, nosep]
    \item Collaborated with a team of 4 engineers to develop internal dashboard tools using React and Node.js.
    \item Wrote unit and integration tests using Jest, increasing code coverage from 60\% to 85\%.
    \item Automated daily data reporting tasks using Python scripts, saving the operations team 5 hours per week.
\end{itemize}

\end{document}
