\documentclass[11pt, a4paper]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{palatino}

\titleformat{\section}{\Large\bfseries\color}{}{0em}{}[\vspace{-0.5ex}\rule{\textwidth}{0.5pt}]
\titlespacing{\section}{0pt}{2ex}{1ex}

\begin{document}
\pagestyle{empty}

\begin{flushleft}
    {\Huge \textbf{Carmen Soler}} \\
    \vspace{1ex}
    \textbf{Lead Backend Engineer \& Distributed Systems Expert} \\
    \vspace{0.5ex}
    Barcelona, Spain $|$ carmen.soler@email.com $|$ \href{https://linkedin.com/in/carmensoler}{linkedin.com/in/carmensoler}
\end{flushleft}

\vspace{-2ex}
\section*{Profile}
Systems-focused engineering leader with 8+ years of experience in designing, building, and scaling high-availability backend infrastructures. Proven track record of leading cross-functional teams, migrating monolithic architectures to microservices, and fostering a culture of engineering excellence and continuous delivery.

\section*{Core Competencies}
\begin{itemize}[leftmargin=0.2in, label={-}, nosep, itemsep=2pt]
    \item \textbf{Languages:} Go, Rust, Java, Python, Bash.
    \item \textbf{Architecture:} Microservices, Event-Driven Architecture, gRPC, RESTful APIs, System Design.
    \item \textbf{Infrastructure:} Kubernetes, Docker, Terraform, AWS (EKS, RDS, DynamoDB), GCP.
    \item \textbf{Data \& Messaging:} PostgreSQL, Redis, Apache Kafka, RabbitMQ, Elasticsearch.
\end{itemize}

\section*{Professional Experience}
\textbf{Staff Software Engineer / Backend Lead} \hfill Mar 2021 -- Present \\
\textit{FinTech Solutions Inc.} \hfill Remote
\begin{itemize}[leftmargin=0.2in, nosep, itemsep=2pt]
    \item Lead a team of 8 backend engineers in overhauling the core transaction processing engine, migrating from a legacy Java monolith to highly concurrent Go microservices.
    \item Improved system throughput by 400\% while reducing latency by 60\%, successfully handling over 10,000 transactions per second during peak loads.
    \item Designed and implemented a robust event-driven architecture using Apache Kafka to ensure zero-data-loss asynchronous processing.
    \item Mentored senior and mid-level engineers, established coding standards, and implemented automated CI/CD pipelines using GitHub Actions and ArgoCD.
\end{itemize}
\vspace{1.5ex}

\textbf{Senior Backend Engineer} \hfill Feb 2018 -- Feb 2021 \\
\textit{CloudStream Networks} \hfill Barcelona, Spain
\begin{itemize}[leftmargin=0.2in, nosep, itemsep=2pt]
    \item Architected a distributed caching layer using Redis Cluster, reducing database load by 70\% and dramatically improving API response times.
    \item Authored Terraform modules to standardize cloud infrastructure provisioning across multiple development and production environments.
    \item Resolved critical performance bottlenecks by profiling and optimizing high-traffic REST endpoints.
\end{itemize}

\section*{Open Source \& Speaking}
\begin{itemize}[leftmargin=0.2in, label={-}, nosep, itemsep=2pt]
    \item \textbf{Core Contributor:} Actively contribute to open-source Go libraries focused on concurrent data processing.
    \item \textbf{Speaker:} "Scaling Event-Driven Systems with Kafka and Go" at GopherCon Europe 2023.
\end{itemize}

\end{document}
