\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in,right=0.75in,top=0.75in,bottom=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{1ex}{1ex}

\begin{document}
\pagestyle{empty}

\begin{center}
    \textbf{\Huge Maria Garcia} \\
    \vspace{0.5ex}
    Barcelona, Spain $|$ \href{mailto:maria.garcia@email.com}{maria.garcia@email.com} $|$ +34 600 000 000 \\
    \href{https://linkedin.com/in/mariagarcia}{linkedin.com/in/mariagarcia} $|$ \href{https://github.com/mariagarcia}{github.com/mariagarcia}
\end{center}

\section*{Professional Summary}
Dedicated and results-driven Software Engineer with over 4 years of experience designing, developing, and maintaining scalable web applications and distributed systems. Proficient in Python, Java, and cloud technologies, with a strong commitment to writing clean, maintainable code and optimizing system performance.

\section*{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Languages:} Python, Java, JavaScript, TypeScript, SQL, HTML/CSS
    \item \textbf{Frameworks \& Libraries:} React, Node.js, Spring Boot, Django, FastAPI
    \item \textbf{Tools \& Cloud:} Docker, Kubernetes, AWS (EC2, S3, RDS), Git, Jenkins, CI/CD pipelines
    \item \textbf{Methodologies:} Agile, Scrum, Test-Driven Development (TDD), Microservices architecture
\end{itemize}

\section*{Experience}
\noindent
\textbf{Senior Software Engineer} \hfill Jan 2024 -- Present \\
\textit{TechInnovate Solutions} \hfill Barcelona, Spain
\begin{itemize}[leftmargin=0.25in]
    \item Architected and implemented scalable microservices using Python and FastAPI, resulting in a 30\% improvement in system response time.
    \item Led the migration of legacy monolithic applications to a containerized Docker and Kubernetes environment on AWS.
    \item Mentored junior developers, conducted code reviews, and championed best practices for testing and deployment.
\end{itemize}

\vspace{1ex}
\noindent
\textbf{Software Engineer} \hfill Jun 2021 -- Dec 2023 \\
\textit{Global Data Systems} \hfill Barcelona, Spain
\begin{itemize}[leftmargin=0.25in]
    \item Developed highly responsive user interfaces using React and Redux, improving overall user engagement by 20\%.
    \item Built robust RESTful APIs with Java and Spring Boot to support front-end functionality.
    \item Optimized complex SQL queries, reducing database load times by up to 40\%.
    \item Collaborated closely with product managers and designers to deliver features on schedule within Agile sprints.
\end{itemize}

\section*{Education}
\noindent
\textbf{Universitat Politècnica de Catalunya} \hfill Sep 2017 -- Jun 2021 \\
\textit{Bachelor of Science in Computer Engineering} \hfill Barcelona, Spain

\section*{Projects}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Real-Time Chat Application:} Built a scalable real-time chat application using Node.js, WebSockets, and Redis for pub/sub messaging. Containerized the application using Docker.
    \item \textbf{E-commerce Analytics Dashboard:} Developed a full-stack dashboard utilizing React and Django to visualize sales data and user metrics, deploying the platform to AWS.
\end{itemize}

\end{document}
